Operational Feature Selection with Gaussian Mixture Models for remote sensing images

### 2016-10-12 paper.tex
add figure of mean nb of selected var

    \begin{figure}[!t]
        \centering
        \begin{tikzpicture}
            \begin{axis}[ymin=0.2,ymax=0.9,grid,axis x line=left,axis y line=left,xlabel={\# variables},ylabel={Cohen's kappa},small]
                \addplot[thick,black] table[x=nb,y=crit] {criterion_1000spl_aisa.txt};
                % \draw[thick,red] (axis cs:15,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:15,\pgfkeysvalueof{/pgfplots/ymax});
                % \draw[thick,black] (axis cs:30,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:30,\pgfkeysvalueof{/pgfplots/ymax});
            \end{axis};
            % \begin{axis}[ymin=0.2,ymax=0.75,grid,axis x line=left,axis y line=left,xlabel={\# variables},ylabel={Cohen's kappa},small]
            %     \addplot[thick,black] table[x=nb,y=crit] {criterion_1000spl.txt};
            %     \draw[thick,red] (axis cs:15,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:15,\pgfkeysvalueof{/pgfplots/ymax});
            %     \draw[thick,black] (axis cs:47,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:47,\pgfkeysvalueof{/pgfplots/ymax});
            % \end{axis};
            % \begin{axis}[ymin=0.2,ymax=0.75,grid,axis x line=left,axis y line=left,xlabel={\# variables},ylabel={Cohen's kappa}]
            %     \addplot[thick,black] table[x=nb,y=crit] {criterion_50000spl.txt};
            %     \draw[thick,red] (axis cs:31,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:31,\pgfkeysvalueof{/pgfplots/ymax});
            %     \draw[thick,black] (axis cs:31,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:31,\pgfkeysvalueof{/pgfplots/ymax});
            % \end{axis};
        \end{tikzpicture}
        \caption{Criterion evolution in function of the number of selected variables for first trial with Aisa dataset. Red vertical line is the retained number of variables and black vertical line is the maximum of the criterion.\label{fig:crit-evol}}
    \end{figure}

@@

    When creating training and validation  sets, special care is taken
    to assure that training samples are picked out from distinct areas
    than test  samples.  The  polygons of the  reference are  split in
    smaller polygons and then 50\%  of the polygons are taken randomly
    for training and the remaining 50\% for validation.  An example of
    training      and     validation      set     is      shown     in
    Figure~\ref{fig:set-aisa}.  From the  training  polygons, a  given
    number of samples  were selected to build the  training set, while
    all  the pixels  from the  validation polygons  were used  for the
    validation.  Moreover 20  random trials were run  with a different
    training  set (different  polygons).  Table~\ref{tab:aisa-otbsimu}
    presents  the results  of the  experiment with  mean and  standard
    deviation  of  the  Kappa  coefficient  over  the  20  trials  and
    Table~\ref{tab:aisa-otbsimu-time}  the   corresponding  processing
    time.

@@

>>>>

    \begin{figure}[!t]
        \centering
        \begin{tikzpicture}
            \begin{axis}[ymin=0.2,ymax=0.9,grid,axis x line=left,axis y line=left,xlabel={\# variables},ylabel={Cohen's kappa},small]
                \addplot[thick,black] table[x=nb,y=crit] {criterion_1000spl_aisa.txt};
                \draw[thick,red] (axis cs:18,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:18,\pgfkeysvalueof{/pgfplots/ymax});
                \draw[thick,black] (axis cs:24,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:24,\pgfkeysvalueof{/pgfplots/ymax});
            \end{axis};
            % \begin{axis}[ymin=0.2,ymax=0.75,grid,axis x line=left,axis y line=left,xlabel={\# variables},ylabel={Cohen's kappa},small]
            %     \addplot[thick,black] table[x=nb,y=crit] {criterion_1000spl.txt};
            %     \draw[thick,red] (axis cs:15,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:15,\pgfkeysvalueof{/pgfplots/ymax});
            %     \draw[thick,black] (axis cs:47,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:47,\pgfkeysvalueof{/pgfplots/ymax});
            % \end{axis};
            % \begin{axis}[ymin=0.2,ymax=0.75,grid,axis x line=left,axis y line=left,xlabel={\# variables},ylabel={Cohen's kappa}]
            %     \addplot[thick,black] table[x=nb,y=crit] {criterion_50000spl.txt};
            %     \draw[thick,red] (axis cs:31,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:31,\pgfkeysvalueof{/pgfplots/ymax});
            %     \draw[thick,black] (axis cs:31,\pgfkeysvalueof{/pgfplots/ymin}) -- (axis cs:31,\pgfkeysvalueof{/pgfplots/ymax});
            % \end{axis};
        \end{tikzpicture}
        \caption{Criterion evolution (kappa) in function of the number of selected variables for first trial with Aisa dataset with 500 samples by class. Red vertical line is the retained number of variables and black vertical line is the maximum of the criterion.\label{fig:crit-evol}}
    \end{figure}

@@

    When creating training and validation  sets, special care is taken
    to assure that training samples are picked out from distinct areas
    than test  samples.  The  polygons of the  reference are  split in
    smaller polygons and then 50\%  of the polygons are taken randomly
    for training and the remaining 50\% for validation.  An example of
    training      and     validation      set     is      shown     in
    Figure~\ref{fig:set-aisa}.  From the  training  polygons, a  given
    number of samples  were selected to build the  training set, while
    all  the pixels  from the  validation polygons  were used  for the
    validation.  Moreover 20  random trials were run  with a different
    training  set (different  polygons).  Table~\ref{tab:aisa-otbsimu}
    presents  the results  of the  experiment with  mean and  standard
    deviation  of  the  Kappa  coefficient  over  the  20  trials  and
    Table~\ref{tab:aisa-otbsimu-time}  the   corresponding  processing
    time. Additionally, Figure~\ref{fig:meanNbVar-aisa} summarizes the mean of the number of selected variables for each variation of the GMM classifier with selection.

@@

    \begin{figure}
      \centering
      \begin{tikzpicture}
        \begin{axis}[ylabel=$\bar{n}_s$,ymax=250,
          symbolic x coords={0,250,500,1000,1050},
          enlargelimits=0.15,legend pos=outer north east,xtick=data,legend cell align=left,
          ybar,
          bar width=5pt,grid,xlabel=Number of training samples per class,small,area legend]
          \addplot coordinates {(250,15.9) (500,21.85) (1000,26.65)};
          \addplot coordinates {(250,11.95) (500,12) (1000,12.05)};
          \addplot coordinates {(250,11.95) (500,12) (1000,12.05)};
          \addplot[red,very thick,sharp plot,update limits=false]coordinates {(0,252) (1050,252)};
          \legend{{\footnotesize SFS kappa},{\footnotesize SFS JM},{\footnotesize SFFS JM}}
        \end{axis}
      \end{tikzpicture}
      \caption{Mean number $\bar{n}_s$ of selected features for the different variation of selection methods for Aisa data set. The red line indicates the original number of spectral features.}
      \label{fig:meanNbVar-aisa}
    \end{figure}
